|

### 2024-10-24 output/seminar-slideshow.qmd
Add FA path diagrams

```{r libraries}
library(tibble)
library(dplyr, warn.conflicts = FALSE)
library(knitr)

@@

>>>>

```{r libraries}
#| include: false

library(tibble)
library(dplyr)
library(knitr)
library(tidyr)
library(ggplot2)
library(lavaan)
library(semPlot)
```

@@

```{r simple-complex-structure}
ITEM_BASE_LOADING <- 1
ITEM_DIST         <- 0.2

simple_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',    ITEM_BASE_LOADING,
  'I2',  'F1',    ITEM_BASE_LOADING + ITEM_DIST,
  'I3',  'F1',    ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I4',  'F2',    ITEM_BASE_LOADING,
  'I5',  'F2',    ITEM_BASE_LOADING + ITEM_DIST,
  'I6',  'F2',    ITEM_BASE_LOADING + 2 * ITEM_DIST
)
complex_item_loadings <- simple_item_loadings                                |>
  bind_rows(tibble(item = 'I3', factor = 'F2', loading = ITEM_BASE_LOADING)) |>
  complete(item, factor, fill = list(loading = 0))

simple_item_loadings <- simple_item_loadings |>
  complete(item, factor, fill = list(loading = 0))

# TODO: Syntax from tibble
simple_spec <- "
  F1 =~ I1 + I2 + I3
  F2 =~ I4 + I5 + I6

  F1 ~~ F2
"
complex_spec <- "
  F1 =~ I1 + I2 + I3
  F2 =~ I3 + I4 + I5 + I6

  F1 ~~ F2
"

simple_spec      |>
  semPlotModel() |>
  semPaths(
    edge.color     = "black",
    residuals      = FALSE,
    thresholds     = FALSE,
    intercepts     = FALSE,
    fixedStyle     = 1,
    whatLabels     = "std"
  )

simple_item_loadings |>
  pivot_wider(names_from = factor, values_from = loading) |>
  ggplot(mapping = aes(F1, F2)) +
  geom_point(size = I(4))

complex_spec     |>
  semPlotModel() |>
  semPaths(
    edge.color     = c(
      "black" |> rep(3),
      PALETTE_RASPBERRY["normal"], # cross-loading
      "black" |> rep(3)
    ),
    residuals      = FALSE,
    thresholds     = FALSE,
    intercepts     = FALSE,
    fixedStyle     = 1,
    whatLabels     = "std",
  )
```
